% Document for tutorial 3
\documentclass[12pt]{scrartcl}
\title{The life of Brian}
\author{John Doe
\thanks{Third year CMP student}}
\begin{document}
\maketitle
\begin{abstract}
	The Life of Brian is not really interesting but I am
	paid to do this job. No one would remember Brian's
	life if not for a mad lecturer who used it as an
	illustrative example in a tutorial at the University
	of East Anglia.
\end{abstract}

\section{Introduction}
Everyone knows, even the dumbest reader, that Brian was
an ordinary bloke.
\section{Infancy}
As Albert Einstein, Brian was a late developer, except
that, contrary to Einstein, Brian never developed very
much.

\subsection{Before the age of six}
Absolutely nothing happened to Brian until the age of
six\ldots{} and not much after.
\subsubsection{Do we need to elaborate?}
No!
\section*{Acknowledgement}
The help of the Brian Trust was \emph{unvaluable} in writing
this paper.

\textbf{Absolutely \emph{nothing} happened} to Brian
until the age of six\ldots{} and not much after

In \texttt{C++} you print ‘‘hello world’’
by using the statement.
\begin{center}
	\texttt{cout << "hello world" << endl;}
\end{center}

You can use a number of environments to create
lists.
\begin{itemize}
	\item Bullet point lists (like this one)
	use the \emph{itemize environment}.
	\item Numbered lists use the
	\emph{enumerate environment}.
	\item Lists that are indexed by words use
	the \emph{description environment}.
\end{itemize}


My program for today:
\begin{enumerate}
	\item Finish this tutorial on \LaTeX.
	\item Have a nap.
	\item Start another tutorial.
\end{enumerate}


Computer languages are classified as follows:
\begin{description}
	\item[C] a language for nerds
	\item[Java] a language for people who do not understand
	pointers
	\item[C++] a language for super-nerds
	\item[Prolog] a language for aliens
\end{description}

Difference between languages:
\begin{itemize}
	\item C is a \emph{procedural} language:
	\begin{itemize}
		\item This is a low level language used to implement
		OS.
		\item The programmer has to manage the dynamic memory.
	\end{itemize}
	\item Java is an \emph{object oriented} language:
	\begin{enumerate}
		\item Pointers are hidden to the user.
		\item Dynamic memory is managed by the system.
	\end{enumerate}
\end{itemize}


There is a lot of wisdom in popular sayings about
the weather.
You probably know this famous proverb:
\begin{quote}
	Red sky at night, shepherd’s delight.\\
	Red sky in morning, fisherman’s warning.
\end{quote}
but did you know this French one:
\begin{quote}
	Rain in November, Christmas in December.
\end{quote}

\end{document}